MetaTracts - A Method for Robust Extraction and Visualization of Carbon Fiber Bundles in Fiber Reinforced Composites

### 2014-12-10 chapters/MetaTracts.tex
new commands for modified text (added, replaced, removed, replacedWith)

\section {User Evaluation}
\label {sec:user_eval}
\begin{figure}[tb]
	\centering
	\includegraphics[width=\linewidth,  trim = 0mm 00mm 0mm 0mm, clip]{images_pvis/usereval.pdf}
	%\includegraphics[width=0.5\textwidth,  trim = 10mm 40mm 0mm 15mm, clip]{imagesMT2014/image_length_histogram.pdf}
	\caption{The user evaluation consists of a set of queries on videos of our results, volume rendering and Hessian colormap. The questionnaire tests the effectiveness of MetaTracts in visualizing ``geometric structure" and ``spatial context". The Likert scale goes from 1-5: strongly disagree, disagree, neutral, agree and strongly agree. }
	\label{fig:userstudy}
\end{figure}
Four NDT practitioners who are familiar with X-Ray computed tomography and its visual representations, four material scientists who are experienced in analyzing fiber reinforced polymers and four practitioners of visualization participated in the user evaluation of our work. We setup a questionnaire with questions on solving given tasks as well as questions using the Likert scale (LS) for evaluating the performance of the MetaTracts over currently used techniques. LS consists of 5 levels from ``strongly disagree" to ``strongly agree". Figure~\ref{fig:userstudy} shows the results in the sequential order they were asked. Task 1 of the questionnaire was to ``identify the number of fiber bundles" from a video showing a 360 degree rotation of the volume rendering of dataset 1 (Figure~\ref{fig:data-char}a). This task tests the perception of geometric structure and how common problems like uniform grayscale values and occlusion of the different fiber bundles affects the user. Figure~\ref{fig:userstudy} shows that, as expected the participants found it difficult to determine the number of bundles from volume rendering alone. Another common approach is to color map the top eigenvector of Hessian matrix to RGB space. We show a video showing a 360 degree rotation of the volume rendering of the color mapped eigenvectors (similar to Figure~\ref{fig:reliable_hessian}a) and asked the same query. Compared to the volume rendering, the Hessian color map provides more information about the major orientations and we see that the evaluators performed better in this test than in the direct volume rendering test. The majority of our participants agreed or strongly agreed (LS) that Hessian color map was more effective. Finally, we showed the MetaTracts extracted bundles (for orientation 1 and 2 separately Figure~\ref{fig:orientation_clustering}d,e). All participants could correctly identify the number of fiber bundles. All participants agreed that MetaTracts was more effective in perceiving geometric structure than direct volume rendering. They especially liked the two dimensional slices of the MetaTracts (Figure~\ref{fig:crop-16-decomp}b, compared to Figure~\ref{fig:data-char}c).
The next set of tasks on the MetaTracts results tests the spatial context perceived from MetaTracts. We achieve this by asking the evaluators to select the largest fiber bundle from a subset of fiber bundles, to select the smallest from a subset and given a fiber bundle and to select the most similar one from a subset. Due to the problems of occlusions and similar grayscale values these tests are difficult on volume rendering of the plain data only, but straight forward using MetaTracts. In the Likert scale, the majority strongly agreed that the tasks are undemanding compared to volume rendering.
Finally, the majority participants agreed that the extracted meshes provides better spatial context than volume rendering.

@@

\section{Limitations and future work}
\label{sec:conclusions}
\color{red}
 A key assumption of the method is ``connectivity'' (Sec.~\ref{sec:char_data}).
If the ``connectivity'' is not satisfied due to noise in the image, the then MetaTracts will be inaccurate. 
The clustering process also assumes that the fiber bundles have a minimum width.
\color{green}
In this paper, we introduce a framework to extract and visualize fiber bundles in composite materials. We show that our framework works at comparatively low resolution and with dense fiber arrangements (when extracting single fibers might not be possible). It handles complex fiber patterns such as ``cross overs'' and ``braiding''. We perform an user evaluation to indicate the usefulness of the method.
\color{black} In future, we plan to increase the precision of the extractions, include uncertainty based visualization to better portray the surface of separations and speed up extraction times.
%
%\begin{figure}
%  \centering
%  \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-scalar.eps}}
%  \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-tracks-1.eps}}
%  \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-tracks-clus-a.eps}}
%    \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-tracks-clus-b.eps}}
%  \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-labels-all.eps}}
%  \caption{Dense data set with bundles which are flat and thin. (a) shows the results original dataset, (b) shows the results of metaTract extraction, (c) shows the results of our two step clustering  into 14 classes. (d) shows the results of voxelization  and (e) shows the results of surface extraction. }\label{fig:crop-6}
%\end{figure}
%% if specified like this the section will be ommitted in review mode

>>>>

\section {User Evaluation}
\label {sec:user_eval}
\begin{figure}[tb]
	\centering
	\includegraphics[width=\linewidth,  trim = 0mm 00mm 0mm 0mm, clip]{images_pvis/usereval_AMA.pdf}
	%\includegraphics[width=0.5\textwidth,  trim = 10mm 40mm 0mm 15mm, clip]{imagesMT2014/image_length_histogram.pdf}
	\caption{The user evaluation consists of a set of queries on videos of our results, volume rendering and Hessian colormap. The questionnaire tests the effectiveness of MetaTracts in visualizing ``geometric structure" and ``spatial context". The Likert scale goes from 1-5: strongly disagree, disagree, neutral, agree and strongly agree. }
	\label{fig:userstudy}
\end{figure}
Four NDT practitioners who are familiar with X-Ray computed tomography and its visual representations, four material scientists who are experienced in analyzing fiber reinforced polymers and four practitioners of visualization participated in the user evaluation of our work. We setup a questionnaire with questions on solving given tasks as well as questions using the Likert scale (LS) for evaluating the performance of the MetaTracts over currently used techniques. LS consists of 5 levels from ``strongly disagree" to ``strongly agree". Figure~\ref{fig:userstudy} shows the results in the sequential order they were asked. Task 1 of the questionnaire was to ``identify the number of fiber bundles" from a video showing a 360 degree rotation of the volume rendering of dataset 1 (Figure~\ref{fig:data-char}a). This task tests the perception of geometric structure and how common problems like uniform grayscale values and occlusion of the different fiber bundles affects the user. Figure~\ref{fig:userstudy} shows that, as expected the participants found it difficult to determine the number of bundles from volume rendering alone. Another common approach is to color map the top eigenvector of Hessian matrix to RGB space. We show a video showing a 360 degree rotation of the volume rendering of the color mapped eigenvectors (similar to Figure~\ref{fig:reliable_hessian}a) and asked the same query. Compared to the volume rendering, the Hessian color map provides more information about the major orientations and we see that the evaluators performed better in this test than in the direct volume rendering test. The majority of our participants agreed or strongly agreed (LS) that Hessian color map was more effective. Finally, we showed the MetaTracts extracted bundles (for orientation 1 and 2 separately Figure~\ref{fig:orientation_clustering}d,e). All participants could correctly identify the number of fiber bundles. All participants agreed that MetaTracts was more effective in perceiving geometric structure than direct volume rendering. They especially liked the two dimensional slices of the MetaTracts (Figure~\ref{fig:crop-16-decomp}b, compared to Figure~\ref{fig:data-char}c).
The next set of tasks on the MetaTracts results tests the spatial context perceived from MetaTracts. We achieve this by asking the evaluators to select the largest fiber bundle from a subset of fiber bundles, to select the smallest from a subset and given a fiber bundle and to select the most similar one from a subset. Due to the problems of occlusions and similar grayscale values these tests are difficult on volume rendering of the plain data only, but straight forward using MetaTracts. In the Likert scale, the majority strongly agreed that the tasks are undemanding compared to volume rendering.
Finally, the majority participants agreed that the extracted meshes provides better spatial context than volume rendering.

@@

\section{Limitations and future work}
\label{sec:conclusions}
\added{
A key assumption of the method is ``connectivity'' (Sec.~\ref{sec:char_data}).
If the ``connectivity'' is not satisfied due to noise in the image, the then MetaTracts will be inaccurate. 
The clustering process also assumes that the fiber bundles have a minimum width.
}
\removed{
In this paper, we introduce a framework to extract and visualize fiber bundles in composite materials. We show that our framework works at comparatively low resolution and with dense fiber arrangements (when extracting single fibers might not be possible). It handles complex fiber patterns such as ``cross overs'' and ``braiding''. We perform an user evaluation to indicate the usefulness of the method.
}
In future, we plan to increase the precision of the extractions, include uncertainty based visualization to better portray the surface of separations and speed up extraction times.
%
%\begin{figure}
%  \centering
%  \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-scalar.eps}}
%  \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-tracks-1.eps}}
%  \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-tracks-clus-a.eps}}
%    \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-tracks-clus-b.eps}}
%  \subfloat[]{\includegraphics[width=0.2\linewidth]{imagesMetaTracts/crop-6-labels-all.eps}}
%  \caption{Dense data set with bundles which are flat and thin. (a) shows the results original dataset, (b) shows the results of metaTract extraction, (c) shows the results of our two step clustering  into 14 classes. (d) shows the results of voxelization  and (e) shows the results of surface extraction. }\label{fig:crop-6}
%\end{figure}
%% if specified like this the section will be ommitted in review mode
